My English activity log

### 2020-03-13 _posts/2019-11-04-my-english-activity-log/my-english-activity-log.Rmd
article 6 + jusqu'au 15/02/2020
article 8 + jusqu'au 13/03 + logo à gauche

author:
  - name: Aurélie Pinchart
date: 12-15-2019
preview: english.jpg
output:
  distill::distill_article:
    self_contained: false
---

@@

>>>>

author:
  - name: Aurélie Pinchart
date: 03-13-2020
preview: english.jpg
output:
  distill::distill_article:
    self_contained: false
---

@@

* **08/02/2020** : I watched a video about plant structure https://www.youtube.com/watch?v=CNGn1qQCn4c.

* **09/02/2020** : I watched a video about nitrogen cycle https://www.youtube.com/watch?v=jzrPiq3YuBM.

## March

* **07/03/2020** : I watched a video about plantibodies https://www.youtube.com/watch?v=gSLwVGHa6uM.

* **09/03/2020** : I watched a video about hypotonic and hypertonic solutions https://www.youtube.com/watch?v=FU9xE8rxnOo.

* **13/03/2020** : I watched a video about drug addiction and phsychoactive drugs https://www.youtube.com/watch?v=zhA1AB5yHmI.
